SMASH companion source code repository

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

This repository contains source code and data accompanying our manuscript,

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).

@@

## Citing this work

If you find any of the source code in this repository useful for your
work, please cite our paper:

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
> Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
> signals.* [arXiv:1709.10066][smash-preprint].

@@

The following analyses generate some of the empirical results
presented in [Xing & Stephens (2016)][smashr-preprint]. If you
encounter a problem running any of the R code in these examples,
please post an [issue][issues].

>>>>

This repository contains data and R source code accompanying our
manuscript,

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
signals.* [arXiv:1709.10066][smash-preprint].

If you find any of the source code in this repository useful for your
work, please cite our paper.

@@

@@

The following analyses generate some of the empirical results
presented in [Xing & Stephens (2016)][smash-preprint]. If you
encounter a problem running any of the R code in these examples,
please post an [issue][issues].
